---
title: "cm101 Notes and Exercises"
author: "Amanda Cheung"
date: "10/24/2017"
output: github_document
---
## Regular expressions and character data

### Challenge warm up
True of False? Why?
```{r}
my_string4 <- 'my_string'
my_string5 <- 'my string'
my_string6 <- "my_string"
my_string4 == my_string5
my_string5 == my_string6
```

### Load pacakges
```{r}
library(singer)
places <- unique(singer_locations$city) ## return vector of unique cities, no repetitions
  
str(places) ## structure
nchar(c("City", "double", "a very long string")) ## number of characters in a string
nchar(c("", NA, " ", "      ", " a ","  ", "\t")) ## white spaces are counted

## \t is a tab, string before is a copy and pasted tab
## don't always trust nchar!
```

## The tools of the trade

```{r}
library(tidyverse)
library(stringr)
library(glue)
```

glueing `glue()`

```{r}
my_name <- "Amanda"
my_age <- 21
my_colour <- "blue"

glue("My name is {my_name}.", " My age two years ago was {my_age - 2}.")
```

```{r}
paste("My name is",my_name,", My age two years ago was ",my_age - 2)
## paste and glue are similar
```

```{r}
glue("
My name is
  {my_name},
My age two years ago was
  {my_age - 2}.")
```

### Challenge

Phrase : Today is Wednesday, October 29, 1986 and the sun shines

Sys.Date()
glue()

```{r}
Sys.Date()
```

```{r}
phrase <- "Today is {today_date} and the sun shines"
glue(phrase,
     today_date = Sys.Date())
```

```{r}
glue(phrase,
     today_date = format(Sys.Date(), "%A, %B %d, %Y"))
```

'glue_data'

```{r}
singer_locations %>% 
  glue_data("{artist_name} is from {city}.") %>% 
  head()
```

## Stringr

```{r}
getNamespaceExports("stringr")
```

```{r}
library(htmlwidgets)
getNamespaceExports("stringr") %>% 
  str_view("str_")
```


```{r}
getNamespaceExports("stringr") %>% 
  str_subset("str_")
```

### Challenge

```{r}
places <- unique(singer_locations$city)
```

And, let's get all the places containing the string "york".

```{r}
places %>%
  str_to_lower() %>% 
  str_subset("york")
```

### Regular Expressions

```{r}
places %>% 
  str_subset("[Yy]ork") ## whatever is inside []

## and lowercase "ork"
## there is an instance with all caps, so the one below and above have an extra result
```

```{r}
places %>% 
  str_subset(coll("york", ignore_case = TRUE))
```

```{r}
places %>% 
  str_subset("York$") ## where york ends the string
```

```{r}
places %>% 
  str_subset("^York") ## where york starts the string
```


### Challenge

Get all places where their name contains some digits. 

```{r}
places %>% 
  str_subset("[:digit:]")
```

```{r}
places %>% 
  str_subset("B.a") ## has the character B and then a
```

```{r}
places %>% 
  str_subset("B.a?") ## has the character B and then 0 or 1 a
```

```{r}
places %>% 
  str_subset("[Nn]ew [Yy]ork")
```




